---
title: "HW 03 - Legos"
author: "Your Name"
date:  "Today's Date"
output: 
  html_document: 
    theme: cerulean
---

This homework assignment reviews some of the data wrangling skills we have been working on the past several weeks.

# Packages

In this assignment we will work with the `tidyverse` as usual:

```{r load-package, message = FALSE}
library(tidyverse)
```

## Lego sales

The data set `lego_sales` contains simulated lego set purchases in the U.S., based on actual prices, for the year 2018. The data set is called `lego_sales` and you can load it using the following code:
```{r load-data}
load(file = "lego_sales.rda")
```
Each row in the data set represents a lego set purchase.  The variables in this data set are as follows:

**first_name**:  first name of customer

**last_name**:  last name of customer

**age**:  age of customer

**phone_number**:  phone number of customer

**set_id**:  ID of lego set purchased

**number**:  item number of lego set purchased

**theme**:  theme of lego set purchased

**subtheme**:  sub-theme of lego set purchased

**year**:  year of purchase

**name**:  name of lego set purchased

**pieces**:  number of pieces of legos in set purchased

**us_price**:  price of set purchased, in U.S. dollars

**image_url**:  image url of lego set purchased

**quantity**:  quantity of lego sets purchased

----------

**Instructions:  Answer the following questions using pipelines. For each question, state your answer in a sentence, e.g. "The first three common names of purchasers are ...".**

1. What are the three most common first names of purchasers?

2. What are the three most common themes of lego sets purchased?

3. Among the most common three themes of lego sets purchased, what is the most common 
subtheme?  *Hint:*  use your answer from question 2 to filter the data.


4. Create a new variable called `age_group` and group the ages into the 
following categories: "18 and under", "19 - 25", "26 - 35", "36 - 50", "51 and over".  *Hint:* Use the `case_when()` function: [case-when-doc](https://www.rdocumentation.org/packages/dplyr/versions/0.7.8/topics/case_when)


5. Which age group has purchased the highest total number of lego sets? *Hint:* some purchases are for more than one lego set, so it is not sufficient to just count the number of observations in each age category.


6. Which age group has spent the most money on legos?

7. Come up with a question you want to answer using these data, and write it down. 
Then, create a data visualization that answers the question, and explain how 
your visualization answers the question.

**Finishing Up:  Be sure to knit one last time and push your final .Rmd and .html files to your repository.  Also, please create a pdf file of your html file and push that as well.**


